Cudele: A File System with Programmable Consistency and Durability

### 2017-03-30 paper/paper.tex
paper: submit abstract and touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: popperize graphs and fix links
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: edit section 3
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: wordsmith and push related work backwards
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: jeff intro comments v0
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% Template: http://www.acm.org/publications/proceedings-template
\documentclass[sigconf]{acmart}
\usepackage{booktabs} % For formal tables
\usepackage{minted}
\usepackage{graphicx}
\usepackage{arydshln}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

\begin{document}
\title{Cudele: Programmable Consistency and Fault Tolerance}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

@@

\input{sections/1_introduction}
%\input{sections/2_related_work}
\input{sections/3_posix_overheads}
\input{sections/4_methodology}
\input{sections/5_implementation}
\input{sections/6_results}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}

>>>>

% Template: http://www.acm.org/publications/proceedings-template
\documentclass[sigconf, preprint]{acmart}
\usepackage{booktabs} % For formal tables
\usepackage{minted}
\usepackage{graphicx}
\usepackage{arydshln}
\usepackage{subcaption}

%% Copyright
%%\setcopyright{none}
%%\setcopyright{acmcopyright}
%%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%%\setcopyright{usgov}
%%\setcopyright{usgovmixed}
%%\setcopyright{cagov}
%%\setcopyright{cagovmixed}
%
%
%% DOI
%\acmDOI{10.475/123_4}
%
%% ISBN
%\acmISBN{123-4567-24-567/08/06}
%
%%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}

\begin{document}
\title{Cudele: A File System with Programmable Consistency and Durability}

@@

%%
%% The code below should be generated by the tool at
%% http://dl.acm.org/ccs.cfm
%% Please copy and paste the code instead of the example below. 
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>  
%\end{CCSXML}
%
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}
%
%% We no longer use \terms command
%%\terms{Theory}
%
%\keywords{ACM proceedings, \LaTeX, text tagging}

@@

\input{sections/1_introduction}
\input{sections/3_posix_overheads}
\input{sections/4_methodology}
\input{sections/5_implementation}
\input{sections/6_results}
\input{sections/2_related_work}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

### 2017-03-30 paper/sections/0_abstract.tex
paper: jeff intro comments v0
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC file systems are abandoning POSIX because the synchronization and
serialization overheads are too costly -- and often uneccessary -- for their
applications.  We provide an API for the client to (1) merge updates into the
global namespace and (2) assign policies to subtrees so that other clients
cannot interfere with the decoupled namespace.  This allows administrators to
optimize subtrees within the same namespace for different workloads. We draw
conclusions about the performance impact of previously unexplored
consistency/durability metadata designs and show that consistency can cause a
104\(\times\) slow down while merging updates (7\(\times\) slow down) and
maintaining durability (\(10\times\) slow down) have a more reasonable cost.

>>>>

HPC developers debate abandoning POSIX because the synchronization and
serialization overheads of providing strong consistency and durability are too
costly -- and often uneccessary -- for their applications.  Unfortunately,
designing near-POSIX file systems excludes applications that rely on strong
consistency or durability, forcing developers to re-write their applications or
deploy them on a different system.  We present a file system and API that
allows clients to specify their consistency/durability requirements and assign
them to subtrees in the namespace, allowing administrators to optimize subtrees
within the same namespace for different workloads.  We draw conclusions about
the performance impact of unexplored consistency/durability metadata designs
and show that strong consistency can cause a 104\(\times\) slow down while merging
updates (7\(\times\) slow down) and maintaining durability (\(10\times\) slow
down) have more reasonable costs.

### 2017-03-30 paper/sections/1_introduction.tex
paper: jeff intro comments v0
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
Today's client-server based file system metadata services have scalability
problems. It takes a lot of resources to service POSIX metadata requests so
applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is expensive and complicated. This problem is
exacerbated by current trends in HPC.  Architectures are transitioning from
complex storage stacks with burst buffer, file system, object store, and tape
tiers to a more simplified stack with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}; this puts more pressure on data access
instead of data movement.

% What is HPC doing?
HPC's unique requirements for file systems ({\it e.g.}, fast creates) and well
defined workloads ({\it e.g.}, workloads) make relaxing POSIX sensible. Without
the constraints of strong consistency and durability, HPC systems can now do
more client side processing with an emphasis on serverless metadata services.
One popular approach is to ``decouple the namespace", where clients lock the
subtree they want exclusive access to so other clients cannot interfere. This
delayed merge ({\it i.e.} a form of eventual consistency) and relaxed
durability improves performance and scalability by avoiding the costs of RPCs,
synchronization, false sharing, and serialization.  While the performance
benefits are obvious for these users, applications that rely on stronger
consistency or durability guarantees must be re-written or deployed on a
different system. The consistency and durability semantics for these systems is
shown in Table~\ref{table:namespaces}.

>>>>

% What is the problem?
File system metadata services in HPC have scalability problems. It has been
shown that HPC workloads, especially checkpoint-restart jobs, are resource
intensive primarily due to contention for the same directories and inodes ({\it
e.g.}, path traversal). Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current trends in HPC, where architectures are transitioning from complex
storage stacks with burst buffer, file system, object store, and tape tiers to
more simplified stackis with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}; this puts more pressure on data access
instead of data movement.

% What is HPC doing?
HPC's unique requirements for file systems ({\it e.g.}, fast creates) and well
defined workloads ({\it e.g.}, workflows) have given rise to file systems with
weaker consistency constraints than POSIX and less durability than programmers
are accustomed to.  Without these constraints, HPC systems can do more
client side processing with an emphasis on serverless metadata services.

One popular approach for relaxing consistency and durability is to ``decouple
the namespace", where clients lock the subtree they want exclusive access to so
other clients cannot interfere. This delayed merge ({\it i.e.} a form of
eventual consistency) and relaxed durability improves performance and
scalability by avoiding the costs of RPCs, synchronization, false sharing, and
serialization.  While the performance benefits are obvious for these users,
applications that rely on stronger consistency or durability guarantees must be
re-written or deployed on a different system. The consistency and durability
semantics for these systems is shown in Table~\ref{table:namespaces}.
